Rule Synthesis for Rule-based Intrusion Detectors

### 2020-05-19 paper/paper.tex
pass on IV (preamble)

\vspace{1ex}
\noindent\textbf{Overview.}~\tname\ takes on input one or more
examples of an attack and produces on output a ranked list of
\emph{plausible rules}---\ie{}, rules that isolate the malicious
traffic produced by the attacks from the benign
traffic. Figure~\ref{fig:overview} shows the workflow of \tname{} as a
pipeline of three components, appearing numbered in the figure.
Public data sets of benign
traffic~\cite{tcpreplay,stratosphere-normal} and rules
exist~\cite{emerging-threats-open}. Consequently, a user of \tname{}
only needs to provide examples of attacks on input.

@@

\tname\ works as follows. First, it creates a rule that captures the
malicious traffic produced by the examples provided on input. In this
step, \tname\ detects options directly from the input messages (see
Section~\ref{sec:rules-and-packets}). More precisely, it creates a
rule containing options that are guaranteed to be satisfied by the
malicious traffic. Let us refer to that rule as the \emph{seed rule}
and its corresponding set of options as \emph{seed options}. Note
that, as only the malicious traffic is considered in this step, the
seed rule is likely over-specified, \ie{}, it may be more restrictive
than necessary. Consequently, the use of that rule could result in
false negatives. Second, \tname\ generates alternative rules that 1)
weaken the constraints expressed in the seed rule while 2) still
capturing the malicious traffic. Given that every option declared in a
rule needs to be satisfied for a rule to capture an attack, any subset
of the set of seed options, by definition, captures the attack
characterized by the malicious traffic. \tname{} leverages that
observation to search for plausible rules containing a proper subset
of options from the seed options. However, note that that approach
alone could result in false positives as it imposes no limit on the
extent the constraints induced from the rule can be weakened. \tname{}
uses benign traffic for that purpose. More precisely, it searches for
plausible rules derived from the seed rule obtained in the previous
step. Finally, \tname{} uses heuristic functions, obtained from a data
set of existing rules, to rank the generated plausible rules by their
similarity to existing rules. Similarity is used to approximate user's
intent. The following sections detail each component of \tname.

>>>>

\vspace{1ex}
\noindent\textbf{Overview.}~\tname\ takes on input one or more
examples of an attack and produces on output a ranked list of
\emph{plausible rules}, \ie{}, rules that captures only the malicious
traffic produced by the attacks. Figure~\ref{fig:overview} shows the workflow of \tname{} as a
pipeline of three components, appearing numbered in the figure.
Public data sets of benign
traffic~\cite{tcpreplay,stratosphere-normal} and rules
exist~\cite{emerging-threats-open}. Consequently, a user of \tname{}
only needs to provide examples of attacks on input.

@@

% (see Section~\ref{sec:rules-and-packets})

%% However, note that that
%% approach alone could result in false positives as it imposes no limit
%% on the extent that the rules can be weakened.  More precisely, it
%% searches for plausible rules derived from the seed rule obtained in
%% the previous step.

\tname\ works as follows. First, it creates a rule that captures the
malicious traffic associated with example attacks provided on
input. In this step, \tname\ detects options directly from the input
messages. More precisely, it creates a rule containing options that
are guaranteed to be satisfied by the malicious traffic. We refer to
that rule as the \emph{seed rule} and its corresponding set of options
as \emph{seed options}. It is important to note that, because only the
malicious traffic is considered in this step, the seed rule is
potentially over-specified, \ie{}, it may be more restrictive than
necessary. Consequently, the use of that rule could result in false
negatives. Second, \tname\ uses benign traffic to generate alternative
rules that 1) weaken the constraints expressed in the seed rule while
2) still capturing the malicious traffic. Given that every option
declared in a rule needs to be satisfied for a rule to capture an
attack, any subset of the set of seed options, by definition, captures
the attack characterized by the malicious traffic. \tname{} leverages
that observation to search for plausible rules containing a proper
subset of options from the seed options that captures \emph{only} the
malicious traffic. Finally, \tname{} uses heuristic functions,
obtained from a data set of existing rules, to rank the generated
plausible rules by their similarity to existing rules. Similarity is
used to approximate user's intent. The following sections detail each
component of \tname.
